Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
pres arcep finie
Ajout des références delaunay et gabriel

    This database \cite{main_database} contains all the information needed to the application of the method. It is from
    \acrfull{arcep}, which is a french national organisation that

    The fields that are being used here are described in Table~\ref{data_columns}

@@

\subsection{Delaunay triangulation}
\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 [citer l'article].

@@

Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969[citer].

>>>>

    This database \cite{main_database} contains all the information needed to the application of the method. It is from
    \acrfull{arcep}, which is an independent French administrative authority responsible for regulating electronic and postal communications and press distribution.

    The fields that are being used here are described in Table~\ref{data_columns}.

@@

\subsection{Delaunay triangulation}
\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 \cite{art_delaunay}.

@@

Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{art_gabriel}.
